---
title: "Survival Analysis of HIV Treatment Efficacy"
subtitle: "Comparative Analysis of 3-Drug vs 2-Drug Regimens"
author: "Sanne Glastra"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document:
    latex_engine: xelatex
---

# Data Preparation

### global settings
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

### read libraries
```{r}
library(tableone)
library(officer)
library(flextable)
library(ggsurvfit)
library(survival)
library(tibble)
library(dplyr)
```

### read csv
```{r}
data <- read.csv("hiv_clinical_trial_data.csv")
```

### recode variables
```{r}
# raceeth variable -- combine variables
data$raceth <- ifelse(data$raceth %in% c(3, 4, 5, 6), 3, data$raceth)

# ivdrug variable -- combine variables
data$ivdrug <- ifelse(data$ivdrug %in% c(2, 3), 2, data$ivdrug)

# karnof variable -- combine variables
data$karnof <- ifelse(data$karnof %in% c(80, 70), 80, data$karnof)
```

### define outcome variables
```{r}
# define pfs variables
data$time_pfs <- data$time
data$censor_pfs <- data$censor

# define os variables
data$time_os <- data$time_d
data$censor_os <- data$censor_d
```


# Create Table 1: Baseline Characteristics
```{r}
# specify which variables want to use in table 1
allVars = c("sex", "raceth", "age", "karnof","strat2", "cd4", "ivdrug", "hemophil","priorzdv")

# specify which variables are categorical variables
catVars = c("sex", "raceth", "ivdrug", "hemophil", "strat2", "karnof")

# Define labels for categorical variables
sex_levels <- c("1" = "Male", "2" = "Female")
raceth_levels <- c(
  "1" = "White Non-Hispanic",
  "2" = "Black Non-Hispanic",
  "3" = "Other/unknown")
ivdrug_levels <- c("1" = "Never", "2" = "Currently/Previously")
hemophil_levels <- c("1" = "Yes", "0" = "No")
strat2_levels <- c("0" = "CD4 ≤ 50", "1" = "CD4 > 50")
karnof_levels <- c(
  "100" = "No evidence of disease",
  "90" = "Minor signs/symptoms of disease",
  "80" = "Some signs/symptoms of disease or cares for self")
tx_levels <- c("1" = "Three-drug regimen including IDV", "0" = "Two-drug regimen without IDV")

# Convert categorical variables to factors
data1 <- data
data1$sex <- factor(data$sex, levels = names(sex_levels), labels = sex_levels)
data1$raceth <- factor(data$raceth, levels = names(raceth_levels), labels = raceth_levels)
data1$ivdrug <- factor(data$ivdrug, levels = names(ivdrug_levels), labels = ivdrug_levels)
data1$hemophil <- factor(data$hemophil, levels = names(hemophil_levels), labels = hemophil_levels)
data1$strat2 <- factor(data$strat2, levels = names(strat2_levels), labels = strat2_levels)
data1$karnof <- factor(data$karnof, levels = names(karnof_levels), labels = karnof_levels)
data1$tx <- factor(data$tx, levels = names(tx_levels), labels = tx_levels)


# create baseline table 
descriptives_tableone <- tableone::CreateTableOne(data = data1, 
                                                  vars = allVars,
                                                  factorVars = catVars,
                                                  strata = "tx",
                                                  test = T,
                                                  addOverall = TRUE)

# print baseline table (showing all levels and using median(iqr))
descriptives_tableone <- print(descriptives_tableone,
                               nonnormal = allVars, # specify which variables to use median(iqr)
                               showAllLevels = TRUE)

# print table to word
descriptives_tableone %>% 
  as.data.frame() %>% 
  rownames_to_column("Characteristic") %>%
  flextable() %>%
  # Bold headers
  bold(part = "header") %>%
  # Set font to Times New Roman, size to 12
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  # Add borders only below the header and in specific locations
  hline_top(border = fp_border(color = "black", width = 1.5), part = "header") %>%
  hline_bottom(border = fp_border(color = "black", width = 1.5), part = "body") %>% # Bottom border
  # Add padding for readability
  padding(padding = 5, part = "all") %>% 
  flextable::save_as_docx(path = "descriptives_tableone.docx") 
```


# Survival Curve Analysis and Log-Rank
### PFS treatment comparison
```{r}
survfit2(Surv(time_pfs, censor_pfs)~tx, data=data1) %>%
  ggsurvfit() +
  add_censor_mark() +
  add_pvalue(location="annotation",
             caption="Log-rank {p.value}") +
  labs(title = "Kaplan-Meier Survival Curves - Progression Free Survival (PFS)")  
```

### OS treatment comparison
```{r}
survfit2(Surv(time_os, censor_os)~tx, data=data1) %>%
  ggsurvfit() +
  add_censor_mark() +
  add_pvalue(location="annotation",
             caption="Log-rank {p.value}") +
  labs(title = "Kaplan-Meier Survival Curves - Overall Survival (OS)")  
```


# Univariate Analysis - PFS 

### process categorical data so it can be read correctly by cox model
```{r}
# make all categorical data into factors
data = data %>%
  mutate(sex = factor(sex,levels=c("1","2")),
         tx = factor(tx,levels=c("0","1")),
         raceth = factor(raceth,levels=c("3","1","2")),
         karnof = factor(karnof,levels=c("80","90", "100")),
         strat2 = factor(strat2,levels=c("0","1")),
         ivdrug = factor(ivdrug,levels=c("1","2")),
         hemophil = factor(hemophil,levels=c("0","1")))
```


### fit cox model for each covariate individually 
```{r}
# treatment
fit_tx_pfs = coxph(Surv(time_pfs, censor_pfs)~tx,data=data,
            ties="efron")

# age
fit_age_pfs = coxph(Surv(time_pfs, censor_pfs)~age,data=data,
            ties="efron")
# sex
fit_sex_pfs = coxph(Surv(time_pfs, censor_pfs)~sex,data=data,
            ties="efron")

# race / ethnicity
fit_raceth_pfs = coxph(Surv(time_pfs, censor_pfs)~raceth,data=data,
            ties="efron")

# karnofsky performance scale
fit_karnof_pfs = coxph(Surv(time_pfs, censor_pfs)~karnof,data=data,
            ties="efron")

# cd4 stratum at screening
fit_strat2_pfs = coxph(Surv(time_pfs, censor_pfs)~strat2,data=data,
            ties="efron")

# baseline cd4 count
fit_cd4_pfs = coxph(Surv(time_pfs, censor_pfs)~cd4,data=data,
            ties="efron")

# iv drug use history
fit_ivdrug_pfs = coxph(Surv(time_pfs, censor_pfs)~ivdrug,data=data,
            ties="efron")

# hemophiliac
fit_hemophil_pfs = coxph(Surv(time_pfs, censor_pfs)~hemophil,data=data,
            ties="efron")

# months of prior zdv use
fit_priorzdv_pfs = coxph(Surv(time_pfs, censor_pfs)~priorzdv,data=data,
            ties="efron")
```


### place all HR / CI results into table and export to word
```{r}
# make a list of all models
models <- list(
  tx = fit_tx_pfs,
  age = fit_age_pfs,
  sex = fit_sex_pfs,
  raceth = fit_raceth_pfs,
  karnof = fit_karnof_pfs,
  strat2 = fit_strat2_pfs,
  cd4 = fit_cd4_pfs,
  ivdrug = fit_ivdrug_pfs,
  hemophil = fit_hemophil_pfs,
  priorzdv = fit_priorzdv_pfs
)

# function to extract exp(coef) and 95% CI 
extract_coefs <- function(fit) {
  summary_fit <- summary(fit)
  exp_coef <- summary_fit$coefficients[, "exp(coef)"]
  lower_95 <- summary_fit$conf.int[, "lower .95"]
  upper_95 <- summary_fit$conf.int[, "upper .95"]
  p_value <- summary(fit)$coefficients[, "Pr(>|z|)"]
  
  return(data.frame(HR = round(exp_coef,2), Lower_CI = round(lower_95,2), Upper_CI = round(upper_95, 2),
                    P_Value = round(p_value,3)))
}

# apply the extraction function and combine into single dataframe
results_list <- lapply(models, extract_coefs)
results_df <- do.call(rbind, results_list)
results_df$CI <- paste0("[", results_df$Lower_CI, ", ", results_df$Upper_CI, "]")
  
# print table
univariate_table_pfs <- print(results_df)

# print table to word
univariate_table_pfs %>% 
  select(HR, CI, P_Value) %>% 
  as.data.frame() %>% 
  rownames_to_column("Characteristic") %>%
  flextable() %>%
  # Bold headers
  bold(part = "header") %>%
  # Set font to Times New Roman, size to 12
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  # Add borders only below the header and in specific locations
  hline_top(border = fp_border(color = "black", width = 1.5), part = "header") %>%
  hline_bottom(border = fp_border(color = "black", width = 1.5), part = "body") %>% # Bottom border
  # Add padding for readability
  padding(padding = 5, part = "all") %>% 
  flextable::save_as_docx(path = "univariate_table_pfs.docx") 
```


# Univariate Analysis - OS 

### fit cox model for each covariate individually 
```{r}
# treatment
fit_tx_os = coxph(Surv(time_os, censor_os)~tx,data=data,
            ties="efron")

# age
fit_age_os = coxph(Surv(time_os, censor_os)~age,data=data,
            ties="efron")
# sex
fit_sex_os = coxph(Surv(time_os, censor_os)~sex,data=data,
            ties="efron")

# race / ethnicity
fit_raceth_os = coxph(Surv(time_os, censor_os)~raceth,data=data,
            ties="efron")

# karnofsky performance scale
fit_karnof_os = coxph(Surv(time_os, censor_os)~karnof,data=data,
            ties="efron")

# cd4 stratum at screening
fit_strat2_os = coxph(Surv(time_os, censor_os)~strat2,data=data,
            ties="efron")

# baseline cd4 count
fit_cd4_os = coxph(Surv(time_os, censor_os)~cd4,data=data,
            ties="efron")

# iv drug use history
fit_ivdrug_os = coxph(Surv(time_os, censor_os)~ivdrug,data=data,
            ties="efron")

# hemophiliac
fit_hemophil_os = coxph(Surv(time_os, censor_os)~hemophil,data=data,
            ties="efron")

# months of prior zdv use
fit_priorzdv_os = coxph(Surv(time_os, censor_os)~priorzdv,data=data,
            ties="efron")
```


### place all HR / CI results into table and export to word
```{r}
# make a list of all models
models <- list(
  tx = fit_tx_os,
  age = fit_age_os,
  sex = fit_sex_os,
  raceth = fit_raceth_os,
  karnof = fit_karnof_os,
  strat2 = fit_strat2_os,
  cd4 = fit_cd4_os,
  ivdrug = fit_ivdrug_os,
  hemophil = fit_hemophil_os,
  priorzdv = fit_priorzdv_os
)

# function to extract exp(coef) and 95% CI 
extract_coefs <- function(fit) {
  summary_fit <- summary(fit)
  exp_coef <- summary_fit$coefficients[, "exp(coef)"]
  lower_95 <- summary_fit$conf.int[, "lower .95"]
  upper_95 <- summary_fit$conf.int[, "upper .95"]
  p_value <- summary(fit)$coefficients[, "Pr(>|z|)"]
  
  return(data.frame(HR = round(exp_coef,2), Lower_CI = round(lower_95,2), Upper_CI = round(upper_95, 2),
                    P_Value = round(p_value,3)))
}

# apply the extraction function and combine into single dataframe
results_list <- lapply(models, extract_coefs)
results_df <- do.call(rbind, results_list)
results_df$CI <- paste0("[", results_df$Lower_CI, ", ", results_df$Upper_CI, "]")

# print table
univariate_table_os <- print(results_df)

# print table to word
univariate_table_os %>% 
  select(HR, CI, P_Value) %>% 
  as.data.frame() %>% 
  rownames_to_column("Characteristic") %>%
  flextable() %>%
  # Bold headers
  bold(part = "header") %>%
  # Set font to Times New Roman, size to 12
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  # Add borders only below the header and in specific locations
  hline_top(border = fp_border(color = "black", width = 1.5), part = "header") %>%
  hline_bottom(border = fp_border(color = "black", width = 1.5), part = "body") %>% # Bottom border
  # Add padding for readability
  padding(padding = 5, part = "all") %>% 
  flextable::save_as_docx(path = "univariate_table_os.docx") 
```

# Multivariate Analysis - PFS

### create different multivariate models (full and reduced)
```{r}
# the following variables were significant in the univariate pfs analysis:
## karnof
## strat2
## cd4

# we will always add tx, age, and sex to our multivariate model

# first, we will fit the full model with all significant / relevant variables from univariate analysis 
full_model <- coxph(Surv(time_pfs, censor_pfs)~tx+age+sex+karnof+strat2+cd4,
                    data = data, ties="efron")

# next, we will try reduced models by removing one variable and comparing it to the full model
## without karnof
reduced_model1 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + strat2 + cd4, data = data) 
## without strat2
reduced_model2 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + karnof + cd4, data = data)
## without cd4
reduced_model3 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + karnof + strat2, data = data)
## without karnof and strat2
reduced_model4 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + cd4, data = data) 
## without karnof and cd4
reduced_model5 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + strat2, data = data)
## without cd4 and strat2
reduced_model6 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + karnof , data = data)
## without cd4, strat2, and karnof
reduced_model7 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex , data = data)

```

### create function to compare full and reduced models 
```{r}
# Function to compare full and reduced models
compare_cox_models <- function(full_model, reduced_model) {
  # Calculate log-likelihood difference
  loglik_diff <- 2 * (logLik(full_model) - logLik(reduced_model))
  
  # Calculate degrees of freedom difference
  df_diff <- attr(logLik(full_model), "df") - attr(logLik(reduced_model), "df")
  
  # Get p-value from chi-squared distribution
  p_value <- pchisq(loglik_diff, df = df_diff, lower.tail = F)
  
  # Print result
  cat("Log-Likelihood Difference: ", loglik_diff, "\n")
  cat("Degrees of Freedom Difference: ", df_diff, "\n")
  cat("p-value: ", p_value, "\n")
}
```

### compare models
```{r}
# full model vs. reduced model 1
compare_cox_models(full_model, reduced_model1) # sign so full model is better

# full model vs. reduced model 2
compare_cox_models(full_model, reduced_model2) # not sign, so can use reduced model

# full model vs. reduced model 3
compare_cox_models(full_model, reduced_model3) # sign so full model is better

# full model vs. reduced model 4
compare_cox_models(full_model, reduced_model4) # sign so full model is better

# full model vs. reduced model 5
compare_cox_models(full_model, reduced_model5) # sign so full model is better

# full model vs. reduced model 6
compare_cox_models(full_model, reduced_model6) # sign so full model is better

# full model vs. reduced model 7
compare_cox_models(full_model, reduced_model7) # sign so full model is better

# therefore, we will continue with reduced model 2

```

### assess confounding
```{r}
# Function to assess confounding based on model coefficients
assess_confounding <- function(full_model, reduced_model) {
  # Extract the coefficients for tx from both models
  tx_full <- full_model$coefficients[1]
  tx_reduced <- reduced_model$coefficients[1]
  
  # Calculate the percent change
  percent_change <- 100 * (tx_reduced - tx_full) / tx_full
  
  # Return the results
  percent_change
}
```

```{r}
# compare reduced_model2 with and without cd4
assess_confounding(reduced_model2, reduced_model6) # percent change is 7.1%

# compare reduced_model2 with and without karnof
assess_confounding(reduced_model2, reduced_model4) # percent change is 0.01%

# both of these percentages are small enough, so we will move on with both cd4 and karnof in our model

```


### assess interaction terms (effect modifiers)
```{r}
reduced_model2_1 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + karnof + cd4 + tx*cd4, 
                          data = data)
# not sign

reduced_model2_2 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + karnof + cd4 + tx*karnof, 
                          data = data)
# not sign

reduced_model2_3 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + karnof + cd4 + tx*sex, 
                          data = data)
# not sign

reduced_model2_4 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + karnof + cd4 + tx*age, 
                          data = data)
# not sign
```

### now we will proceed with our final model
```{r}
reduced_model2 <- coxph(Surv(time_pfs, censor_pfs) ~ tx + age + sex + karnof + cd4, data = data)
summary(reduced_model2)
```

### place all HR / CI results into table and export to word
```{r}
# function to extract exp(coef) and 95% CI 
extract_coefs <- function(fit) {
  summary_fit <- summary(fit)
  exp_coef <- summary_fit$coefficients[, "exp(coef)"]
  lower_95 <- summary_fit$conf.int[, "lower .95"]
  upper_95 <- summary_fit$conf.int[, "upper .95"]
  p_value <- summary(fit)$coefficients[, "Pr(>|z|)"]
  
  return(data.frame(HR = round(exp_coef,2), Lower_CI = round(lower_95,2), Upper_CI = round(upper_95, 2),
                    P_Value = round(p_value,3)))
}

# apply the extraction function and combine into single dataframe
results <- extract_coefs(reduced_model2)
results$CI <- paste0("[", results$Lower_CI, ", ", results$Upper_CI, "]")

# print table
multivariate_table_pfs <- print(results)

# print table to word
multivariate_table_pfs %>% 
  select(HR, CI, P_Value) %>% 
  as.data.frame() %>% 
  rownames_to_column("Characteristic") %>%
  flextable() %>%
  # Bold headers
  bold(part = "header") %>%
  # Set font to Times New Roman, size to 12
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  # Add borders only below the header and in specific locations
  hline_top(border = fp_border(color = "black", width = 1.5), part = "header") %>%
  hline_bottom(border = fp_border(color = "black", width = 1.5), part = "body") %>% # Bottom border
  # Add padding for readability
  padding(padding = 5, part = "all") %>% 
  flextable::save_as_docx(path = "multivariate_table_pfs.docx") 
```

# Multivariate Analysis - OS

### create different multivariate models (full and reduced)
```{r}
# the following variables were significant in the univariate pfs analysis:
## karnof
## strat2
## cd4

# we will always add tx, age, and sex to our multivariate model

# first, we will fit the full model with all significant / relevant variables from univariate analysis 
full_model <- coxph(Surv(time_os, censor_os)~tx+age+sex+karnof+strat2+cd4,
                    data = data, ties="efron")

# next, we will try reduced models by removing one variable and comparing it to the full model
## without karnof
reduced_model1 <- coxph(Surv(time_os, censor_os) ~ tx + age + sex + strat2 + cd4, data = data) 
## without strat2
reduced_model2 <- coxph(Surv(time_os, censor_os) ~ tx + age + sex + karnof + cd4, data = data)
## without cd4
reduced_model3 <- coxph(Surv(time_os, censor_os) ~ tx + age + sex + karnof + strat2, data = data)
## without karnof and strat2
reduced_model4 <- coxph(Surv(time_os, censor_os) ~ tx + age + sex + cd4, data = data) 
## without karnof and cd4
reduced_model5 <- coxph(Surv(time_os, censor_os) ~ tx + age + sex + strat2, data = data)
## without cd4 and strat2
reduced_model6 <- coxph(Surv(time_os, censor_os) ~ tx + age + sex + karnof, data = data)
## without cd4, strat2, and karnof
reduced_model7 <- coxph(Surv(time_os, censor_os) ~ tx + age + sex , data = data)

```

### compare models (using previously created function)
```{r}
# full model vs. reduced model 1
compare_cox_models(full_model, reduced_model1) # sign so full model is better

# full model vs. reduced model 2
compare_cox_models(full_model, reduced_model2) # not sign, so can use reduced model

# full model vs. reduced model 3
compare_cox_models(full_model, reduced_model3) # not sign, so can use reduced model

# full model vs. reduced model 4
compare_cox_models(full_model, reduced_model4) # sign so full model is better

# full model vs. reduced model 5
compare_cox_models(full_model, reduced_model5) # sign so full model is better

# full model vs. reduced model 6
compare_cox_models(full_model, reduced_model6) # sign so full model is better

# full model vs. reduced model 7
compare_cox_models(full_model, reduced_model7) # sign so full model is better

# therefore, we will continue with reduced model 2 and reduced model 3

```

### assess confounding (using previously created function)

```{r}
# compare reduced_model2 with and without cd4
assess_confounding(reduced_model2, reduced_model6) # percent change is 2.0%

# compare reduced_model2 with and without karnof
assess_confounding(reduced_model2, reduced_model4) # percent change is 4.955%

# both of these percentages are small enough, so we will move on with both cd4 and karnof in our model

# compare reduced_model2 with and without strat2
assess_confounding(reduced_model3, reduced_model6) # percent change is 2.53%

# compare reduced_model2 with and without karnof
assess_confounding(reduced_model3, reduced_model4) # percent change is 0.027%

# therefore, both reduced_model2 and reduced_model3 don't have a significant confounders. however, reduced_model3 has less confounding than reduced_model2.

```

### check the significance of covariates in both models to see which ones are more significant

```{r}
summary(reduced_model2)
summary(reduced_model3)

# covariates in reduced_model3 have overall lower p values than in reduced_model3
```

### as a result, even though both reduced_model2 and reduced_model3 are effective models, reduced_model3 has slightly less confounding and slightly more significance

### assess interaction terms (effect modifiers)
```{r}
reduced_model3_1 <- coxph(formula = Surv(time_os, censor_os) ~ tx + age + sex + karnof + strat2 + tx*karnof, data = data)
# not sign

reduced_model3_2 <- coxph(formula = Surv(time_os, censor_os) ~ tx + age + sex + karnof + strat2 + tx*strat2, data = data)
# not sign

reduced_model3_3 <- coxph(formula = Surv(time_os, censor_os) ~ tx + age + sex + karnof + strat2 + tx*age, data = data)
# not sign

reduced_model3_4 <- coxph(formula = Surv(time_os, censor_os) ~ tx + age + sex + karnof + strat2 + tx*sex, data = data)
# not sign
```

### now we will proceed with our final model
```{r}
reduced_model3 <- coxph(Surv(time, censor) ~ tx + age + sex + karnof + strat2, data = data)
summary(reduced_model3)
```

### place all HR / CI results into table and export to word
```{r}
# function to extract exp(coef) and 95% CI 
extract_coefs <- function(fit) {
  summary_fit <- summary(fit)
  exp_coef <- summary_fit$coefficients[, "exp(coef)"]
  lower_95 <- summary_fit$conf.int[, "lower .95"]
  upper_95 <- summary_fit$conf.int[, "upper .95"]
  p_value <- summary(fit)$coefficients[, "Pr(>|z|)"]
  
  return(data.frame(HR = round(exp_coef,2), Lower_CI = round(lower_95,2), Upper_CI = round(upper_95, 2),
                    P_Value = round(p_value,3)))
}

# apply the extraction function and combine into single dataframe
results <- extract_coefs(reduced_model3)
results$CI <- paste0("[", results$Lower_CI, ", ", results$Upper_CI, "]")

# print table
multivariate_table_os <- print(results)

# print table to word
multivariate_table_os %>% 
  select(HR, CI, P_Value) %>% 
  as.data.frame() %>% 
  rownames_to_column("Covariate") %>%
  flextable() %>%
  # Bold headers
  bold(part = "header") %>%
  # Set font to Times New Roman, size to 12
  font(fontname = "Times New Roman", part = "all") %>%
  fontsize(size = 11, part = "all") %>%
  # Add borders only below the header and in specific locations
  hline_top(border = fp_border(color = "black", width = 1.5), part = "header") %>%
  hline_bottom(border = fp_border(color = "black", width = 1.5), part = "body") %>% # Bottom border
  # Add padding for readability
  padding(padding = 5, part = "all") %>% 
  flextable::save_as_docx(path = "multivariate_table_os.docx") 
```
